---
title: "nCoronaVirus_Report"
author: "WY"
date: "2/4/2020"
output:
  github_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Daily Update on the new corona virus statistics [(中文)](https://github.com/Wenlong-Y/New_Corona_Virus/blob/master/Report_CN.md)

The data was obtained from an R package. To insall that R package. Use the following command:

```{r eval=FALSE}
remotes::install_github("GuangchuangYu/nCov2019")
```

Then, I loaded the libraries and data by:
```{r loading libraries and data, message=FALSE, warning=FALSE}
library(nCov2019)
library(utf8)
library(tidyverse)
library(lubridate)
x <- get_nCov2019(lang = "en")
```

We start from two data sets in the packages: total confirmed/suspected/dead/recovered numbers of cases and the changes from the previous day.

We tide up the data with commands below:
```{r data cleaning}
dataDay <- x$chinaDayList %>% mutate(confirm = as.numeric(confirm), suspect = as.numeric(suspect), dead = as.numeric(dead), heal = as.numeric(heal), deathoverconfirm = dead/confirm)
dataDay <- dataDay %>% extract(date,c("month","day"), regex = "^(\\d+)\\.(\\d+)$",remove = FALSE) 
dataDay <- dataDay %>% mutate(month = as.numeric(month), day = as.numeric(day))
dataDay <- dataDay %>% mutate(date = make_date(2020,month,day))

dataAdd <- x$chinaDayAddList %>% mutate(confirm = as.numeric(confirm), suspect = as.numeric(suspect), dead = as.numeric(dead), heal = as.numeric(heal), deathoverconfirm = dead/confirm)
dataAdd <- dataAdd %>% extract(date,c("month","day"), regex = "^(\\d+)\\.(\\d+)$",remove = FALSE) 
dataAdd <- dataAdd %>% mutate(month = as.numeric(month), day = as.numeric(day))
dataAdd <- dataAdd %>% mutate(date = make_date(2020,month,day))

```

The last updated time (Beijing Time)is
```{r}
x$lastUpdateTime
```


Now we present the total number of confirmed and suspected respectively.

```{r}
dataDay %>% ggplot() + geom_point(aes(date,confirm,colour="Confirmed")) +geom_point(aes(date,suspect,color="Suspect")) +theme(legend.position="right")+ylab("Number of cases")+labs(colour="Type")+scale_color_manual(values=c("blue","red"))
```

Now we want to put an upper limit on infected cases, so we add up the confimred and suspected. Because a big portion of suspected cases become confirmed cases. 

It is obvious that starting Jan. 28th, the increase of sum of confirmed and suspected case is on a straight line until Feb. 9th. The line is fitted with data during this period.

```{r}
dataDay <- dataDay %>% mutate(confandsusp = confirm + suspect)
dataforfitting <- dataDay %>% filter(date > make_date(2020,1,27) & date < make_date(2020,2,9)) 
model <- lm(confandsusp ~ date, data=dataforfitting)
dataforfitting2 <- dataDay %>% filter(date > make_date(2020,2,13)) 
model2 <- lm(confandsusp ~ date, data=dataforfitting2)
plot(dataDay$date, dataDay$confandsusp, xlab = "Date", ylab = "confirmed + suspected" )
abline(model)
abline(model2)
mtext(paste("The number of cases (suspected + confirmed) increases", as.character(floor(model$coefficients[2])),"per day on average\n between Jan 28th and Feb 8th. with R-squared value of ",round(summary(model)$r.squared, digits=5),".\n", "After Feb. 13, the number of cases (confirmed+suspect) increases ",as.character(floor(model2$coefficients[2])), "\n with R-squred value of", round(summary(model2)$r.squared, digits=5),"."))
```


Now, we want to calculate the rate of death. There are several ways to do this, one way is to divide the dead by the confirmed cases.

```{r}
dataDay %>% ggplot(aes(date,deathoverconfirm))+geom_point()
```

Another way of calculation is to use dead and recovered as total number of cases that we know the results. Then we could find the portion of cases result in death.

```{r}
dataDay %>% ggplot()+geom_point(aes(date,dead/(heal+dead)))
```

Here are the total dead and healed cases:

```{r}
dataDay %>% ggplot() + geom_point(aes(date,dead,colour="Dead")) +geom_point(aes(date,heal,color="Healed")) +theme(legend.position="right")+ylab("Number of cases")+labs(colour="Type")+scale_color_manual(values=c("black","red"))
```


Now we present the new cases on each day:

```{r}
dataAdd %>% ggplot() + geom_point(aes(date,confirm,colour="Confirmed")) +geom_point(aes(date,suspect,color="Suspect")) +theme(legend.position="right")+ylab("Number of cases")+labs(colour="Type")+scale_color_manual(values=c("blue","red"))
```

And the sum of newly confimred and suspected cases for each day:

```{r}
dataAdd %>% ggplot(aes(date,confirm+suspect))+geom_point()
```

Here are daily numbers of death and recovery:

```{r}
dataAdd %>% ggplot() + geom_point(aes(date,dead,colour="Dead")) +geom_point(aes(date,heal,color="Healed")) +theme(legend.position="right")+ylab("Number of cases")+labs(colour="Type")+scale_color_manual(values=c("black","red"))
```


## Cases by country

We just look at the total number of cases for countries:
```{r, message=FALSE, fig.height=8}
library(grid)
library(gridExtra)
areatotal <- x$areaTree$total %>% select(confirm, suspect, dead, heal,deadRate,healRate)
x$areaTree$name[2] <- "Dimaond ship"
x$areaTree$name[4] <- "Japan homeland"
x$areaTree$name[10] <- "Iran"
areatotal <- (cbind(x$areaTree$name,areatotal) %>% head(25))
names(areatotal)[1] <- "Country"  
grid.table(areatotal)
```

## Cases by Chinese provinces

The death rate for Hubei province and non-Hubei province is provided.

```{r}
deathrate<-x$dailyDeadRateHistory
deathrate <- deathrate %>% mutate(hubeiRate=as.numeric(hubeiRate), notHubeiRate=as.numeric(notHubeiRate), countryRate=as.numeric(countryRate))
deathrate <- deathrate %>% extract(date,c("month","day"), regex = "^(\\d+)\\.(\\d+)$",remove = FALSE) 
deathrate <- deathrate %>% mutate(month = as.numeric(month), day = as.numeric(day))
deathrate <- deathrate %>% mutate(date = make_date(2020,month,day))
deathrate %>% ggplot()+geom_point(aes(date,hubeiRate,color="Hubei Rate"))+geom_point(aes(date,notHubeiRate,color="non-Hubei Rate"))+geom_point(aes(date,countryRate,color="country Rate"))+ ylab("Percentage(%)")
```

Detailed information for each province:

```{r,  warning=FALSE}
y <- load_nCov2019(lang = "en")

```

```{r,fig.height=5}
for(i in 1:34)
{
  grid.text(label = as.character(x[,1]$name[i]),x=0.5,y=.9, gp=gpar(cex=2))
  if(dim(x[i])[1]<10){
  grid.table(x[i] %>% select(name,confirm,dead,heal,deadRate,healRate),vp=viewport(x=0.5,y=.5,width=1,height=1))
  grid.newpage()
  }
  if(dim(x[i])[1]>=10){
  grid.table(x[i] %>% head(10) %>% select(name,confirm,dead,heal,deadRate,healRate),vp=viewport(x=0.5,y=.5,width=1,height=1))
  grid.newpage()
  }
  provs <- as.character(x[,1]$name[i])
  
    if(y$data %>% filter(province==provs) %>% .$city %>% as.factor %>% levels %>% length != 1){
p <- y$data %>% filter(province==provs,city!=provs) %>% group_by(city) %>% ggplot(color=city) + geom_line(aes(time,confirmed,color=city))+geom_point(aes(time,confirmed,color=city))+ylab(paste(provs," confirmed"))
print(p)
grid.newpage()
    }
  
      if(y$data %>% filter(province==provs) %>% .$city %>% as.factor %>% levels %>% length == 1){
p <- y$data %>% filter(province==provs)%>% ggplot(color=city) + geom_line(aes(time,confirmed,color=city))+geom_point(aes(time,confirmed,color=city))+ylab(paste(provs," confirmed"))
print(p)
grid.newpage()
    }
  
}
```


