---
title: "CoronaVirus in MASSACHUSETTS"
author: "WY"
date: "3/12/2020"
output:
  github_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The data was obtained from online sources

Here are the total number of confirmed cases and death in Massatuessas and US:
```{r loading libraries and data, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)
library(cowplot)
covMas <- read.csv("covmas.csv")
sources <- read.csv("masSources.csv")
covMasDet <- read.csv("covmasdetail.csv")
covMasDay <- read.csv("covmasday.csv")
covMasAge <- read.csv("covmasAge.csv")
```

Number of confirmed, suspected, total (confirmed+suspected) and death in Massachusetts:


```{r plotting, warning=FALSE, echo=FALSE， message=FALSE}
covMaslong <- gather(covMas %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X), key="key", value="value", -date)
names(covMaslong)[2] <- "Class"
p1 <- covMaslong %>% filter(Class %in% c("presumptive","confirmed","total", "death"))%>% ggplot(aes(date,value,color=Class,shape=Class))+geom_line(size=.5)+geom_point(size=1)+ylab("numbers of people")+xlab("")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
covUS <-read.csv("https://covidtracking.com/api/us/daily.csv")
covUS <- covUS %>% mutate(date = as.Date(as.character(date),"%Y%m%d"), US_confirmed = positive, US_deaths = death) %>% select(date, US_confirmed, US_deaths)
covUSlong <- gather(covUS, key="key", value="value", -date)
names(covUSlong)[2] <- "Class"
p2 <- covUSlong %>% filter(Class %in% c("US_confirmed","US_deaths"))%>% ggplot(aes(date,value,color=Class,shape=Class))+geom_line(size=.5)+geom_point(size=1)+ylab("numbers of people")+xlab("")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
plot_grid(p1, p2, ncol = 1, align = "v")
#ggplotly(p1)
#ggplotly(p2)
```

The daily changes:

```{r plotting for daily changes, warning=FALSE, echo=FALSE}
covMasDaylong <- gather(covMasDay %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X), key="key", value="value", -date)
names(covMasDaylong)[2] <- "Class"
covMasDaylong %>%  ggplot(aes(date,value,color=Class,shape=Class))+geom_line(size=.5)+geom_point(size=1)+ylab("numbers of people")+xlab("")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
#ggplotly(p)
```

Here's some detailed information about the people who are diagnoised positive. Here are the distribution by county:

```{r, echo=FALSE}
covMasDetCntlong <- gather(covMasDet %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X) %>% select(date,Barnstable,Berkshire,Bristol,Dukes, Franklin,Essex,Hampden,Hampshire,Middlesex,Nantucket,Norfolk,Plymouth,Suffolk,Worcester,CntUnknown), key="key", value="value", -date)
names(covMasDetCntlong)[2] <- "County"

covMasDetCntlong %>% ggplot(aes(date, value, color=County))+geom_line(size=.5)+geom_point(size=1)+ylab("numbers of people")+xlab("")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
#ggplotly(p)
```

By gender:

```{r, echo=FALSE}
covMasDetSexlong <- gather(covMasDet %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X) %>% select(date,Male,Female,sexUnknown), key="key", value="value", -date)
names(covMasDetSexlong)[2] <- "Class"
covMasDetSexlong %>% ggplot(aes(date, value, color=Class, shape = Class)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of people") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
#ggplotly(p)
```


Whether the patient is treated in hospital:


```{r, echo=FALSE}
covMasDetHoslong <- gather(covMasDet %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X) %>% select(date,hospitalized,notHospitalized,Hosunknown), key="key", value="value", -date)
names(covMasDetHoslong)[2] <- "Class"
covMasDetHoslong %>% ggplot(aes(date, value, color = Class, shape = Class)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of people") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
#ggplotly(p)
```

By age:

```{r age, warning=FALSE, echo=FALSE}
covMasAgeLong <- gather(covMasAge %>% mutate(date=as.Date(date, "%Y-%m-%d")) %>% select(-X),key="key", value="value", -date)

names(covMasAgeLong)[2] <- "Class"
covMasAgeLong %>% filter(Class %in% c("below19s","Age20s","Age30s", "Age40s", "Age50s", "Age60s", "Age70s", "above80", "ageUnknown"))%>% ggplot(aes(date, value, color = Class)) + geom_line(size = .5) + geom_point(size = 1) + xlab("") + ylab("Number of people infected CovID-19")
#ggplotly(p)
```