---
title: "CoronaVirus in MASSACHUSETTS"
author: "WY"
date: "3/12/2020"
output:
  github_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The data was obtained from online sources

Here are the total number of confirmed cases and death in Massatuessas and US:
```{r loading libraries and data, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)
library(cowplot)
library(downloader)
data_dir = "./data"
dir.create(data_dir)
url_zip <- "https://www.mass.gov/doc/covid-19-raw-data-may-11-2020/download"
download(url_zip, dest="./data/dataset.zip", mode="wb") 

unzip ("./data/dataset.zip", exdir = "./data")
```

Number of confirmed, suspected, total (confirmed+suspected) and death in Massachusetts:


```{r plotting, warning=FALSE, echo=FALSE， message=FALSE}
cases <- read.csv("./data/Cases.csv")
caseslong <- gather(cases %>% mutate(Date=as.Date(Date, "%m/%d/%Y")) %>% select(Date, Cases), key="key", value="value", -Date)
names(caseslong)[2] <- "Category"
p1 <- caseslong %>% ggplot(aes(Date, value, color=Category, shape = Category)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of people") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))

covUS <-read.csv("https://covidtracking.com/api/us/daily.csv")
covUS <- covUS %>% mutate(date = as.Date(as.character(date),"%Y%m%d"), US_confirmed = positive, US_deaths = death) %>% select(date, US_confirmed, US_deaths)
covUSlong <- gather(covUS, key="key", value="value", -date)
names(covUSlong)[2] <- "Class"
p2 <- covUSlong %>% filter(Class %in% c("US_confirmed","US_deaths"))%>% ggplot(aes(date,value,color=Class,shape=Class))+geom_line(size=.5)+geom_point(size=1)+ylab("numbers of people")+xlab("")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
plot_grid(p1, p2, ncol = 1, align = "v")
#ggplotly(p1)
#ggplotly(p2)
```

The daily changes:

```{r plotting for daily changes, warning=FALSE, echo=FALSE}
caseslong <- gather(cases %>% mutate(Date=as.Date(Date, "%m/%d/%Y")) %>% select(Date, New), key="key", value="value", -Date)
names(caseslong)[2] <- "Category"
caseslong %>% ggplot(aes(Date, value, color=Category, shape = Category)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of people") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Accumulated deaths related to Covid-19:

```{r plotting for deaths, warning=FALSE, echo=FALSE}
death <- read.csv("./data/DateofDeath.csv")
death <- death %>% mutate(Date=as.Date(Date.of.Death, "%m/%d/%Y"))
death %>% ggplot(aes(Date, Running.Total)) + geom_line(size = .5) + geom_point(size = 1) + ylab("Acuumulated number of Deaths") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Death per day:

```{r plotting for deaths per day, warning=FALSE, echo=FALSE}
death %>% ggplot(aes(Date, New.Deaths)) + geom_line(size = .5) + geom_point(size = 1) + ylab("Daily New Deaths") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Data related to gender:

```{r plotting for cases by gender, warning=FALSE, echo=FALSE}
sex <- read.csv("./data/Sex.csv")
sexlong <- gather(sex %>% mutate(Date=as.Date(Date, "%m/%d/%Y")), key="key", value="value", -Date)
names(sexlong)[2] <- "Sex"
sexlong %>% ggplot(aes(Date, value, color=Sex, shape = Sex)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of cases") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Data related to age, where the percentage is calculated among people who are/were infected by Covid-19:

```{r plotting for cases by age, warning=FALSE, echo=FALSE}
age <- read.csv("./data/Age.csv")
age <- age %>% mutate(Date=as.Date(Date, "%m/%d/%Y"))
age %>% ggplot(aes(Date, Cases, color=Age)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of people") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
age <- age %>% mutate(rate_Hospitalization = Hospitalized/Cases * 100, rate_Death = Deaths/Cases * 100)
age %>% ggplot(aes(Date, rate_Hospitalization, color=Age)) + geom_line(size = .5) + geom_point(size = 1) + ylab("Percentage of Hospitalization by Age") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
age %>% ggplot(aes(Date, rate_Death, color=Age)) + geom_line(size = .5) + geom_point(size = 1) + ylab("Percentage of Death by Age") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```


Data by County:

```{r plotting for cases by county, warning=FALSE, echo=FALSE}
county <- read.csv("./data/County.csv")
county <- county %>% mutate(Date=as.Date(Date, "%m/%d/%Y"))
county %>% ggplot(aes(Date, Count, color=County)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of cases") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
county %>% filter( Date >as.Date("2020/04/01"))%>% ggplot(aes(Date, Deaths, color=County)) + geom_line(size = .5) + geom_point(size = 1) + ylab("numbers of deaths") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
county <- county %>% mutate(death_rate = Deaths/Count * 100)
county %>% filter( Date >as.Date("2020/04/01"))%>% ggplot(aes(Date, death_rate, color=County)) + geom_line(size = .5) + geom_point(size = 1) + ylab("Percentage") + xlab("") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
